GVN-Hoist: Hoisting Computations from Branches

### 2016-08-19 hoist.tex
analysis

@@

>>>>

Loads are hoisted the most followed by scalars, stores and calls in decreasing
order.  This was the common trend in all our experiments. One reason why loads
are hoisted more than scalars is the early execution of this pass in the llvm
pass pipeline where there are many loads (?? Verify). This order may change should this pass
be scheduled later.

@@

TODO: Table for decrease in the code-size of final binaries.
